A Switching Planner for Combined Task and Observation Planning

### 2010-11-23 subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/prop-dtp.tex
Might still have some algebra wrong, but I think I did some repairing of the reward sketch.
 - Charles

\begin{equation}\label{eq:expectedvalue}
V_{\pp{FSC}}(\bstate) = \Expect \bigg{[} 
\sum_{t=0}^{N}  \reward(\bstate_t) \mid \pp{FSC}, \bstate = \bstate_0 \bigg{]}
\end{equation}

\noindent Where $b_t$ is the belief state at time $t$. Finally, it is
useful to note that there is a corresponding deterministic FSCs for
both sequential (e.g., conformant) and contingent plans.

>>>>

\begin{equation}\label{eq:expectedvalue}
V_{\pp{FSC}}(\bstate) = \Expect \bigg{[} 
\sum_{t=0}^{N-1}  \reward(\bstate_t, \pp{FSC}_t) \mid \pp{FSC}, \bstate = \bstate_0 \bigg{]}
\end{equation}

\noindent Where $b_t$ is the belief-state at step $t$, $\pp{FSC}_t$ is
the action prescribed at step $t$, and

\[\reward(\bstate, \action) = \sum_{\state \in \states}
\bstate(\state)\reward(\state, \action).\]

\noindent Finally, it is
useful to note that there is a corresponding deterministic FSCs for
both sequential (e.g., conformant) and contingent plans.
